---
---
---

# R: The Final Day of Coding Temple Classes.

## Project 1: HR Analytics

### Our premise today will be to intake a dataset from Kaggle, analyse the data, clean, transform, model/stat test, explore(vis).

```{r}
install.packages('tidyverse')
library(tidyverse)
```

```{r}
ndf <- read.csv("C:/Users/jjs61/OneDrive/Desktop/Class/week_7/HR_Analytics.csv")

ndf <- as_tibble(ndf)

ndf


```

# Hypothesis

Ho: Salary and Education don't have a statistical significance to one another Ha: Salary and Education have a statistical significance to one another

Step 2: Tidy Data

```{r}
names(ndf) <- names(ndf) %>% str_to_lower()
names(ndf)

```

```{r}
ndf  %>% summarise(na_count = sum(is.na(ndf)))
colSums(is.na(ndf))
```

If you have a column with null values that pertained to my analysis, you need to explore the data and then come up with a solution. I you try to drop before checking, we may end up missing data that had to do with a relationship

```{r}
View(ndf)
```

```{r}
install.packages('RPostgreSQL')
```

```{r}
dsn_database = "R_data" 

dsn_hostname = "localhost"  
dsn_port = "5432"              
dsn_uid = "postgres"        
dsn_pwd = "sydney187"       
```

```{r}
tryCatch({
    drv <- dbDriver("PostgreSQL")
    print("Connecting to Database…")
    connec <- dbConnect(drv, 
                 dbname = dsn_database,
                 host = dsn_hostname, 
                 port = dsn_port,
                 user = dsn_uid, 
                 password = dsn_pwd)
    print("Database Connected!")
    },
    error=function(cond) {
            print("Unable to connect to Database.")
    })
```

Change columns to be boolean

```{r}
ndf['over18'] <- ndf['over18'] == 'Y'
ndf['overtime'] <- ndf['overtime'] == 'Yes'
ndf['attrition'] <- ndf['attrition'] == 'Yes'
```

```{r}
ndf['businesstravel'] <- ndf['businesstravel'] %>% str_replace_all('_', '_')

```

```{r}
ggplot(data=ndf, aes(x=education, y =monthlyincome)) + 
  geom_point()
```

```{r}
cor(ndf$education, ndf$monthlyincome)*100
```

```{r}
cor(ndf[sapply(ndf,is.numeric)])
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
